% resume.tex
% vim:set ft=tex spell:

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=2.5cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{hyperref}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}


% and the actual content starts here
\begin{document}

{\LARGE \textbf{{\color{blue!50!black}David Roberts}}}\hfill dave.a.roberts@gmail.com

{\hfill 440.503.5974}

\vspace{1em}
\hrule
\vspace{1em}

\subsection*{Certifications}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
	\item[Security Clearance]
	US Citizen with {\color{blue} security clearance}
	\item[PMI ACP:]
	{\color{blue} Agile Certified Practitioner} since September 2012
\end{description*}
\end{indentsection}

\subsection*{Experience}

\begin{itemize}
	\parskip=0.1em


    
  \item
	\headerrow
		{\textbf{General Dynamics Advanced Information Systems}}
		{\textbf{Fairfax, VA}}
	\\
  	\headerrow
		{\emph{Web Developer \& Scrum Master}}
		{\emph{June 2011 -- Present}}
	\begin{itemize*}

  
    \item {\color{blue} Scrum master} and developer for seven person {\color{blue} Agile development} team.
  
    \item Held weekly face-to-face meetings with customer and product owner.  Delivered production-ready software every two weeks.
  
    \item Built indicator database using {\color{blue} Ruby on Rails} / {\color{blue} jQuery} / {\color{blue} CSS} / {\color{blue} PostgreSQL} to coordinate cyber information sharing and manage cyber risks for US-CERT and the Department of Homeland Security
  
    \item Developed on {\color{blue} Linux}, source managed using {\color{blue} Git SCM}, code reviews with {\color{blue} GitLab}, continuous integration using {\color{blue} Jenkins}, {\color{blue} Test Driven Development (TDD)} using {\color{blue} Cucumber} / {\color{blue} RSpec}, deployed using {\color{blue} Capistrano}, and documented using {\color{blue} \LaTeX}.
  
    \item Prototyped storage application for network intrusion prevention and detection system using {\color{blue} PHP CodeIgniter}.
  
    \item My random property {\color{blue} here}.
  
	\end{itemize*}
  

    
  \item
	\headerrow
		{\textbf{EMC (NetWitness)}}
		{\textbf{Reston, VA}}
	\\
  	\headerrow
		{\emph{Software Engineer}}
		{\emph{October 2010 -- June 2011}}
	\begin{itemize*}

  
    \item Produced real-time network forensic engineering software.
  
    \item Developed applications using {\color{blue} Java} / {\color{blue} Spring} / {\color{blue} Hibernate} to monitor and analyze network threats.
  
    \item Maintained client management software used to monitor sensitive information on workplace systems, written in {\color{blue} C$^\sharp$}
  
    \item Utilized {\color{blue} Amazon EC2} cloud services to perform {\color{blue} service oriented architecture} tasks for NetWitness Spectrum. Spectrum was the winner of the 2011 American Business Awards New Product and Service of the Year Stevie Award.
  
	\end{itemize*}
  


\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Education}

\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\textbf{Miami University}}
		{\textbf{Oxford, OH}}
	\\
	\headerrow
		{\emph{Computer Science, Master of Computer Science}}
		{\emph{2005 -- 2007}}
	\begin{itemize*}
		\item Graduated 2007 Cumulative GPA 3.5
		\item Research Area: Interdisciplinary tool between Mechanical Engineering and Systems Analysis to study discontinuous systems
	\end{itemize*}

	\item
	\headerrow
		{\textbf{Miami University}}
		{\textbf{Oxford, OH}}
	\\
	\headerrow
		{\emph{Systems Analysis, Bachelor of Applied Science}}
		{\emph{2001 -- 2005}}
	\begin{itemize*}
		\item Double major: Systems Analysis and Computer Science
    \item Taught supplemental courses to provide help for students taking Java courses
		\item Graduated 2005 \emph{Cum Laude} 3.5 GPA
	\end{itemize*}

\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Projects / Skills}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
	\item[GitHub]
	A full list of my personal projects can be found at \href{http://github.com/daveroberts}{github.com/daveroberts} including:
	\begin{itemize*}
    \item[>] \textbf{Happy Puppy: }I created a simple {\color{blue} MVC PHP} web framework with an Object Relational Mapper (ORM).
    \item[>] \textbf{vim scripting: }Scripting/programs for my {\color{blue} VIM} configuration.
    \item[>] \textbf{RubyScrapers: }Web scrapers used to lift information from websites without an API made with Ruby and Nokogiri.
    \item[>] \textbf{C$^\sharp$ Apps: }Created a simple lexical analyzer and expression parser to improve on the basic calculator in Windows.  Created applications to rename all files in a directory with regular expressions.
	\end{itemize*}
	\item[SQL:]I have used SQL at every job listed in my experience, varying from Access to SQLite to SQL Server.  I also have experience with {\color{blue} NoSQL} solutions such as {\color{blue} MongoDB}.
	\item[Real Time Applications:]I am interested in real time web technologies such as {\color{blue} Meteor}, {\color{blue} Node.js}, and other JavaScript MVC frameworks like {\color{blue} Angular JS} and {\color{blue} backbone.js}  Presently, these frameworks aren't widely used.  If your company uses these frameworks, I am very interested.
	\item[Functional Programming:]I believe in learning multiple programming paradigms.  I have successfully completed the course {\color{blue} Functional Programming Principles in Scala}, taught by the creator of Scala and Java compiler designer Martin Odersky.

\end{description*}
\end{indentsection}

\end{document}
